\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel-space

### 2012-05-01 titlepage.tex
update blurb and keywords

\keywords{FOO, BAR, Computers, Science}

@@

\begin{dedication}
%There is a wondrous fractal nature to all aspects of the universe.

At the time of writing, my life is focused entirely on this one project. There is a vast amount of thought in this thesis, and many more rich worlds lie hidden in each of the open avenues for future work.

Yet it pales in comparison to the scope of a Ph.D. thesis, and even more so next to all the details of a person's entire life.
After I finish this project (whatever that may mean), it will become but a fond memory, a mere building block in a city of even grander things.

>>>>

\keywords{concurrency, verification, kernels}

@@

\begin{dedication}
There is a fractal nature to all aspects of life.

At the time of writing, I am focused entirely on this one project. There is a vast amount of thought in this thesis, and many more rich worlds lie hidden in each of the open avenues for future work.

Yet it pales in comparison to the scope of a Ph.D. thesis, and even more so next to all the details of a person's entire life.
After I finish this project, it will become but a fond memory, a mere building block in a city of even grander things.
